Exacerbated by the Pandemic: Analyzing the Impact of COVID-19 on Mortality Among Toronto's Homeless by Gender Disparities

### 2024-03-17 paper/paper.qmd
paper.qmd

![Deaths by Age Group and Gender](../outputs/figures/age_gender_death.png)
Figure 3: Deaths by Age Group and Genders

@@

![Distribution of Deaths by Age Group](../outputs/figures/yearly_death.png)
Figure 4: Distribution of Deaths by Age Group

![Deaths by Age Group and Gender](../outputs/figures/gender_year_hist.png)
Figure 5:Deaths by Age Group and Gender

@@

## Covid-19 Effect
after covid-19, death count of homeless increase. The bar graph illustrates the comparison of homeless death counts before and after the outbreak of COVID-19, not controlled by any other variables. The period prior to COVID-19 is represented by a significantly lower bar, indicating a lower death count among the homeless population. In contrast, the bar representing the post-COVID period is substantially higher, suggesting a marked increase in the number of deaths. The visualization of data comparison supports the hypothesis that the death count of homeless individuals has increased after the outbreak of the pandemic. It is worthy to note that this data does not differentiate by other variables, such as gender or aged group, implying that the increase in deaths is a general trend influencing the homeless population as a whole. This trend could be attributed to various pandemic-related factors, including increased vulnerability to the virus due to pre-existing health conditions, the strain of medical resources, and other indirect consequences of the global pandemic crisis. 
![Distribution of Deaths by Age Group](../outputs/figures/death_counts_by_covid.png)
Figure 6: Distribution of Deaths by Age Group

@@

![Distribution of Deaths by Age Group](../outputs/figures/death_counts_by_gender_covid.png)
Figure 7: Distribution of Deaths by Age Group

>>>>

![Deaths by Age Group and Gender](../outputs/figures/age_gender_death.png)
Figure 3: Deaths by Age Group and Gender

@@

![Distribution of Deaths by Age Group](../outputs/figures/yearly_death.png)
Figure 4: Yearly Total Death Count

![Deaths by Age Group and Gender](../outputs/figures/gender_year_hist.png)
Figure 5: Yearly Total Death Count by Gender

@@

## Covid-19 Effect
after covid-19, death count of homeless increase. The bar graph illustrates the comparison of homeless death counts before and after the outbreak of COVID-19, not controlled by any other variables. The period prior to COVID-19 is represented by a significantly lower bar, indicating a lower death count among the homeless population. In contrast, the bar representing the post-COVID period is substantially higher, suggesting a marked increase in the number of deaths. The visualization of data comparison supports the hypothesis that the death count of homeless individuals has increased after the outbreak of the pandemic. It is worthy to note that this data does not differentiate by other variables, such as gender or aged group, implying that the increase in deaths is a general trend influencing the homeless population as a whole. This trend could be attributed to various pandemic-related factors, including increased vulnerability to the virus due to pre-existing health conditions, the strain of medical resources, and other indirect consequences of the global pandemic crisis. 
![Distribution of Deaths by Age Group](../outputs/figures/death_counts_by_covid.png)
Figure 6: Death Counts Before and After COVID with 95% CI

@@

![Distribution of Deaths by Age Group](../outputs/figures/death_counts_by_gender_covid.png)
Figure 7: Death Counts by Gender and COVID Period with 95% CI
